relauo Amicus Brief Models

### 2022-05-24 modeling/amicus_type/relauo.Rmd
change relauo model

```{r, eval=F}
#save models for paper tables
saveRDS(mod11, "models/relauo_fetus.rds")
saveRDS(mod23, "models/relauo_undue.rds")
saveRDS(mod26, "models/relauo_abortionregret.rds")

>>>>

```{r, eval=F}
#save models for paper tables
saveRDS(mod11, "models/relauo_fetus.rds")
saveRDS(mod23, "models/relauo_undue.rds")
saveRDS(mod3, "models/relauo_abortionregret.rds")
